Security Vulnerabilities in Neuroimaging Container Images

### 2020-09-10 paper.tex
Improved abstract

\begin{abstract}
Software containers have become key to the deployment of
scientific data analyses on high-performance computing (HPC)
infrastructures, due to their positive impact on the portability, deployment, and
reproducibility of computations. Container images, however, often contain slightly outdated
software packages compared to HPC environments maintained by professional
 system administrators, and they often carry more
software packages than required by analyses, including compilers or unused
system librairies. As a result, container images are likely to contain
important amounts of security vulnerability, increasing the attack surface
for the entire infrastructure. This paper presents a vulnerability analysis
of container images for scientific data analysis. We analyze container
images with four vulnerability scanners, focusing on the use case of
neuroscience data analyses. We quantify the effect of images updates and
size reduction on the number of vulnerabilities, and conclude with
recommendations on how to build container images with a reduced amount of
vulnerabilities.

>>>>

\begin{abstract}
Software containers greatly facilitate the deployment of scientific
data analyses on high-performance computing (HPC) infrastructures, due
to their positive impact on the portability, deployment, and
reproducibility of computations. However, container images often
contain outdated or unnecessary software packages, which increases the
number of security vulnerabilities present in the images, and widens
the attack surface for the entire infrastructure. This paper presents a
vulnerability analysis of container images for scientific data
analysis. We analyze container images with four vulnerability scanners,
focusing on the use case of neuroscience data analyses, and quantifying
the effect of images updates and minification on the number of
vulnerabilities. We conclude with recommendations on how to build
container images with a reduced amount of vulnerabilities.
